---
title: "R Notebook"
author: eyan
date: 25/01/2021
output: html_notebook
---
```{r}
library('tidyverse')
```


```{r}
customers <- read.csv("C:/Users/ruth/Desktop/Olist/olist_customers_dataset.csv")
order.items <- read.csv("C:/Users/ruth/Desktop/Olist/olist_order_items_dataset.csv")
order.payments <- read.csv("C:/Users/ruth/Desktop/Olist/olist_order_payments_dataset.csv")
order.reviews <- read.csv("C:/Users/ruth/Desktop/Olist/olist_order_reviews_dataset.csv")
orders <- read.csv("C:/Users/ruth/Desktop/Olist/olist_orders_dataset.csv")
sellers <- read.csv("C:/Users/ruth/Desktop/Olist/olist_sellers_dataset.csv")
products <- read.csv("C:/Users/ruth/Desktop/Olist/olist_products_dataset.csv")
product.category <- read.csv("C:/Users/ruth/Desktop/Olist/product_category_name_translation.csv")
```

Changing the name of the product column

```{r}
colnames(product.category)[1] <- "product_category_name"
head(product.category)
```
Joining the tables

```{r}
prod <- products %>% inner_join(product.category)

olist <-customers %>%
        inner_join(orders) %>%
        inner_join(order.items) %>%
        inner_join(order.payments) %>%
        inner_join(order.reviews) %>%
        inner_join(sellers) %>%
        inner_join(prod) # %>%
        # inner_join(geolocation,by=c('customer_city'='geolocation_city'))
dim(olist)
```

looking for missing values

```{r}
colSums(is.na(olist))
```

Plotting for missing values
```{r}
library(VIM)
aggr_plot <- aggr(olist, col=c('navyblue','red'), numbers=TRUE, sortVars=TRUE, labels=names(olist), cex.axis=.7, gap=3, ylab=c("Histogram of missing data","Pattern"))
```

Dropping the missing values

```{r}
olist[rownames(na.omit(olist)),]
# rownames(olist)
```

Checking for duplicates

```{r}
anyDuplicated(olist)
```
Dropping irrelevant columns
```{r}
olist.copy <- olist
colnames(olist)
```
```{r}
olist <- olist.copy[,-c(1,2,3,5,6,13,14,15,18,25,23,26,28,29,31,40)]

colnames(olist)
```

Save to a CSV file.

```{r}
write.csv(olist,'olist2.csv')
```

Renaming the columns that are misspelled

```{r}
colnames(olist)[19] <- "product_description_length"
colnames(olist)[18] <- "product_name_length"
colnames(olist)
```

Checking for outliers in the numeric columns

```{r}
#get the numeric columns
num.col <- Filter(is.numeric, olist)
for (i in 1:length(num.col)) {
  boxplot(num.col[,i], main=names(num.col[i]), type="1")
  print(i)
}

```
Removing outliers from selected columns

```{r}
#using the subset function

olist <- subset(olist,price<=5000)
olist <- subset(olist,payment_value<=10000)
olist <- subset(olist,product_weight_g<=35000)
```

```{r}
#get the numeric columns
num.col <- olist[c(9,13,21)]
for (i in 1:length(num.col)) {
  boxplot(num.col[,i], main=names(num.col[i]), type="1")
  print(i)
}

```

UNIVARIATE ANALYSIS

```{r}
#Getting the general overview of the data
summary(olist)
```


```{r}
library(e1071)

desc_stats <- data.frame(
  min = apply(num.col, 2, min),
  median = apply(num.col, 2, median),
  mean_df = apply(num.col, 2, mean),
  SD = apply(num.col, 2, sd),
  max = apply(num.col, 2, max),
  kurt = apply(num.col, 2, kurtosis),
  skew = apply(num.col,2, skewness)
)
desc_stats <- round(desc_stats,1)
head(desc_stats)
```


```{r}
library(dplyr)
library(inspectdf)

inspect_cat(olist)
```
**common_pcnt**, the percentage of each column occupied by the most common level shown in **common.**

## Bivariate Analysis visualization

```{r}
library(corrplot)
corrplot(cor(num.col))
```
